Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-11-19 manuscript/cpcrw_manuscript.Rmd
Restructuring section 4.1

Warming usually increases soil GHG fluxes, for example at depth in a long-term Arctic tundra experiment {Sistla, 2013 #3666}, as increased temperatures enhance the production of extracellular enzymes, increase enzyme activities, and enhance desorption rates of organic matter from minerals. A key question, for both experimentalists and modelers {Falloon, 2011 #3045}, is to what degree such soils' emissions could by constrained by their moisture status, that is itself driven by changes in factors such as high-latitude temperatures, vapor pressure deficit, and precipitation.

@@

In contrast, the temperature sensitivities observed in this experiment were low (all less than 2.0, even when controlling for changes in soil moisture), but not unprecedented in comparison to a wide range of other laboratory soil incubations {Hamdi, 2013 #3664}. It is more typical to observe Q~10~ values of around 2 {Dutta, 2006 #1427}{Schädel, 2016 #4444}, although the temperature sensitivity of C release can change over time of incubation {Dutta, 2006 #1427} and vary between soil fractions cycling over different time horizons {Karhu, 2010 #2503}{Schädel, 2014 #4472}. We observed Q10 change over the course of this incubation, emphasizing the need for longer-term studies {Lee, 2012 #4503}{Elberling, 2013 #3720}.

Observed surface CO~2~ fluxes at this CPCRW site exhibited a Q~10~ of 5.1 ± 1.4 over a temperature range of 3.5-15 °C (personal communication, C. Anderson); these surface fluxes were measured over multiple months and include root respiration, however, confounding any direct comparison. It is also important to note that while increased temperature does not always drive C mineralization rates in forest mineral soils {Giardina, 2000 #2159}, it is linked with increases in soil moisture content can lead to changes in microbial community structure and GHG fluxes {Xue, 2016 #4361}.

>>>>

@@

In contrast, the temperature sensitivities observed in this experiment were low (all less than 2.0, even when controlling for changes in soil moisture), although not unprecedented in comparison to a wide range of other laboratory soil incubations {Hamdi, 2013 #3664}. It is more typical to observe Q~10~ values of around 2 {Dutta, 2006 #1427}{Schädel, 2016 #4444}, although the temperature sensitivity of C release can change over time of incubation {Dutta, 2006 #1427} and vary between soil fractions cycling over different time horizons {Karhu, 2010 #2503}{Schädel, 2014 #4472}. Observed surface CO~2~ fluxes at this CPCRW site exhibited a Q~10~ of 5.1 ± 1.4 over a temperature range of 3.5-15 °C (personal communication, C. Anderson); these surface fluxes were measured over multiple months and include root respiration, however, confounding any direct comparison. It is also important to note that while increased temperature does not always drive C mineralization rates in forest mineral soils {Giardina, 2000 #2159}, it is linked with increases in soil moisture content can lead to changes in microbial community structure and GHG fluxes {Xue, 2016 #4361}.
